Making Sequential Programs Deterministic

### 2019-04-05 experiments.tex
randoop bugs

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex Gradle plugin does not respect those settings.
After that, NonDex ran without problems on Randoop.
NonDex reported no flaky tests.
\todo{Revise the following text.
  I renumbered the bugs without realizing that this section refers to them
  by number, and I don't know which one these refer to any
  more.
  Please use cross-references or macros.  Also, this needs to be expanded
  to account for the additional bugs.}
We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
Bug 1 and Bug 2 have corresponding test cases whereas Bug 3 does not.
As NonDex is a \textit{flaky test} detection tool, Bug 3 is outside of its scope.
The reason for nondeterminism in Bug 2 was a call to the \<System.getProperty()> method which
is not modeled by NonDex.

>>>>

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex Gradle plugin does not respect those settings.
After that, NonDex ran without problems on Randoop.
NonDex reported no flaky tests.
%\todo{Revise the following text.
%  I renumbered the bugs without realizing that this section refers to them
%  by number, and I don't know which one these refer to any
%  more.
%  Please use cross-references or macros.  Also, this needs to be expanded
%  to account for the additional bugs.}
We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
\bugHashSet and \bugClasspath have corresponding test cases whereas \bugTimestampOutput and 
\bugTimestampOutput do not.
As NonDex is a \textit{flaky test} detection tool, detecting \bugTimestampOutput and \bugTimestampOutput 
is outside of its scope.
The reason for nondeterminism in \bugClasspath was a call to the \<System.getProperty()> method which
is not modeled by NonDex.
